### 2023-02-14 manuscript.Rmd
Update manuscript.Rmd
Co-authored-by: Aaron Peikert <aaron.peikert@posteo.de>
Update manuscript.Rmd

# Introduction
Based on four basic principles of a more responsible research assessment in academic hiring and promotion processes [@schonbrodt2022responsible], @gartner2022responsible suggested a specific evaluation scheme for published manuscripts, reusable datasets, and research software.
Gaertner et al. provide evaluation schemes for published manuscripts, published datasets, and software contributions.
We specifically endorse the increased emphasis on research software as recognizable and laudable scientific contribution.
Why are research software contributions important scientific contributions?
We would like to respond with a quote from the Science Code Manifesto (http://sciencecodemanifesto.org/):
"Software is an essential research product, and the effort to produce, maintain, adapt, and curate code must be recognized."
and
"Software is a cornerstone of science. Without software, twenty-first century science would be impossible."
Yet, despite the heavy reliance on computational infrastructure, the current academic infrastructure does not adequately incentivise software development and, specifically, good software engineering practice that we would expect from a research software engineer [@baxter2012research].
Here, we specifically comment on the proposed evaluation scheme for research software contributions (Table 3 of @gartner2022responsible).
While the authors criticize the use of invalid metrics to evaluate publications (Journal Impact Factors, Citations, H-Index), those same metrics (or variants thereof) are mainly relied on in their proposal to evaluate research software.
However, they same critisism applies to those metrics in the context of research software evaluation.
We therefore argue to follow their evaluation scheme for publications: In a first stage, rigor should be evaluated, establishing whether the software product passes a certain treshold, and in the second stage, more complicated dimensions, such as impact, can be evaluated.
In the following, we discuss their proposed criteria.
We then discuss rigor in the context of research software, and propose specific criteria to measure it.
At last, we elaborate on the assessment of impact in the context of research software.

>>>>

# Introduction
Based on four basic principles of a more responsible research assessment in academic hiring and promotion processes [@schonbrodt2022responsible], @gartner2022responsible suggested a specific evaluation scheme for published manuscripts, reusable datasets, and research software.
We specifically endorse the increased emphasis on research software as recognizable and laudable scientific contribution.
Why are research software contributions important scientific contributions?
We would like to respond with a quote from the Science Code Manifesto (http://sciencecodemanifesto.org/):
"Software is a cornerstone of science. Without software, twenty-first century science would be impossible."
and
"Software is an essential research product, and the effort to produce, maintain, adapt, and curate code must be recognized."
Yet, despite the heavy reliance on computational infrastructure, the current academic infrastructure does not adequately incentivise software development and, specifically, good software engineering practice that we would expect from a research software engineer [@baxter2012research].
Here, we specifically comment on the proposed evaluation scheme for research software contributions (Table 3 of @gartner2022responsible).
While the authors criticize the use of invalid metrics to evaluate publications (Journal Impact Factors, Citations, H-Index), those same metrics (or variants thereof) are mainly relied on in their proposal to evaluate research software.
However, they same critisism applies to those metrics in the context of research software evaluation.
We therefore argue to follow their evaluation scheme for publications: In a first stage, rigor should be evaluated, establishing whether the software product passes a certain treshold, and in the second stage, more complicated dimensions, such as impact, can be evaluated.
In the following, we discuss their proposed criteria.
We then discuss rigor in the context of research software, and propose specific criteria to measure it.
At last, we elaborate on the assessment of impact in the context of research software.
